---
title       : Developing Data Products Course Project
subtitle    : Linear regression on the mtcars dataset
author      : Stefan Zaaiman
job         : Super duper data scientist
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
revealjs:
   theme: default
   center: "true"
   transition: concave
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : default      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides
---

## Linear regression on the mtcars dataset

Johns Hopkins University

Bloomberg School of Public Health

Developing Data Products Course Project

Stefan Zaaiman

---

## App overview

* This presentation accompanies the app which can be found [here](https://stefanzaaimanapps.shinyapps.io/stefanapp).
* The source code for the app and this slidify presentation can be found [here](https://github.com/StefanZaaiman/DevDataProdsCourseProj). 
* The user can select any of 3 variables from the mtcars dataset: displacement, weight and quarter mile time.
* The app then automatically conducts a linear regression of this selected variable against mile per gallon.
* The app presents the results of the linear regression as a scatterplot of the predictor (user-selected) and response (mpg) variables, with the fitted linear regression line also plotted on the graph.
* The following 3 slides shows these three graphs (each of these are generated on the fly with R code).

---

## Graph of Displacement vs MPG regression

```{r, echo=FALSE}
library(datasets)
data(mtcars)
names(mtcars) = c("mpg", "cyl", "Displacement", "hp", "drat", "Weight", "QuartermileTime", "vs", "am", "gear", "carb")
plot(mtcars$Displacement, mtcars$mpg, main = "Regression of Displacement and MPG", xlab="Displacement", ylab = "MPG")
abline(lm(mpg~Displacement, data = mtcars))
```

---

## Graph of Weight vs MPG regression

```{r, echo=FALSE}
library(datasets)
data(mtcars)
names(mtcars) = c("mpg", "cyl", "Displacement", "hp", "drat", "Weight", "QuartermileTime", "vs", "am", "gear", "carb")
plot(mtcars$Weight, mtcars$mpg, main = "Regression of Weight and MPG", xlab="Weight", ylab = "MPG")
abline(lm(mpg~Weight, data = mtcars))
```

---

## Graph of Quartermile Time vs MPG regression

```{r, echo=FALSE}
library(datasets)
data(mtcars)
names(mtcars) = c("mpg", "cyl", "Displacement", "hp", "drat", "Weight", "QuartermileTime", "vs", "am", "gear", "carb")
plot(mtcars$QuartermileTime, mtcars$mpg, main = "Regression of Quartermile Time and MPG", xlab="Quartermile Time", ylab = "MPG")
abline(lm(mpg~QuartermileTime, data = mtcars))
```

